Looking Back: One Year HPC Certification Forum

### 2019-04-11 paper.tex
New structure

  We have developed a first version of an HPC certification program that would clearly categorize, define, and examine competences.
  Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
  Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
  From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
  Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.
\end{abstract}

@@

This article describes the current status of the certification program by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.

Our previous work described the evolution from the bootstraping project towards the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.

>>>>

  With the HPC Certification Forum we aim to clearly categorize, define, and examine competences which brings benefit to all stakeholders involved in training.
  In this paper, we report the status and progress this independent body has made during the first year of its existence.
  Particularly, in various directions drafts of processes and prototypes have been generated to create a holistic ecosystem that will mature over this year.
\end{abstract}

@@

This article describes the current status of the certification program by looking back for the one year of this independent body that curate the competences and aims to issue certificates for the users.
Our previous work described the evolution from the project that sparked the initial activity that lead to the independent body of the HPC Certification forum \cite{TAHCPKHHSS19}.

\section{The HPC Certification Forum}

\section{Skill Organization}

\subsection{Skill Example}

\section{Certification}

\subsection{Examination Process}

\section{Ecosystem}

\subsection{Linking Training Material}

\subsection{Supportive Tools}

\section{Discussion of the Benefits}

Making clear what skills are required of or recommended for a competent HPC user would benefit both the HPC service providers and practitioners.
Moreover, it would allow centres to bundle together skills that are most beneficial for specific user roles and scientific domains.
From the perspective of content providers, existing training material can be mapped to competences allowing users to quickly identify and learn the skills they require.
Finally, the certificates recognized by the whole HPC community simplify inter-comparison of independently offered courses and provide additional incentive for participation.

\section{Conclusion}
